Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis

### 2018-02-06 paper.tex
A few small changes.
Started 48-72 hours section of Results

\paragraph{24-48 hours}
During the RI period within the eye, $N^2$ generally decreased above 16 km and increased below (Fig.~\ref{fig:stab-24-48}a).
These tendencies at the innermost radii were driven almost entirely by advection (Fig.~\ref{fig:stab-24-48}b); vertical turbulence (Fig.~\ref{fig:stab-24-48}c) and radiation (Fig.~\ref{fig:stab-24-48}d) contributed negligibly to the static stability tendencies in this region.
Outside of the eye, meanwhile, the $N^2$ evolution exhibited alternating layers of positive and negative tendencies.
Near and above 18 km existed an upward-sloping region of decreasing $N^2$ that extended out to the 180-km radius.
In this region, neither vertical turbulence nor radiation exhibited negative $N^2$ tendencies; advection was the only forcing for destabilization.
Immediately below this layer was a region of increasing $N^2$, which sloped upward from 17 km near the 30-km radius to just below 18 km outside of the 100 km radius.
Advection and vertical turbulence both contributed to this positive $N^2$ tendency, with advection playing an important role below about 17.5 km and and turbulence playing an important role above.
The sum of advection and turbulence (Fig.~\ref{fig:stab-24-48}e) reveals two discontiguous regions of increasing $N^2$ rather than one contiguous region.
The addition of radiation to these two terms, however, (Fig.~\ref{fig:stab-24-48}f) provides the link between these two regions, indicating that radiation also plays a role in strengthening the stable layer just above the tropopause.
Below 17 km, a horizontally-extensive layer of decreasing $N^2$ also was forced by a combination of advection, vertical turbulence, and radiation.
The sum of advection and vertical turbulence accounts only for two isolated regions of decreasing $N^2$ in this layer, and actually forces stabilization in part of the region.
For example, just above 16 km in the 150-200-km radial band, the sum of advection and vertical turbulence forces an increase in $N^2$.
Likewise, throughout most of the 30-60-km radial band in this layer, advection and vertical turbulence combine to force near-zero or positive $N^2$ tendencies.
Radiative tendencies overcome this forcing for stabilization in both of these regions to produce the radially-extensive region of destabilization just below the tropopause.

@@

Dunion et al. speculate that the diurnal pulse only occurs in mature storms. Maybe the development of the near-tropopause stable layer could partially explain the reason for this.
% text...
% \section{Section title}

>>>>

\paragraph{24-48 hours}
During the RI period, $N^2$ within the eye generally decreased above 16 km and increased below (Fig.~\ref{fig:stab-24-48}a).
These tendencies at the innermost radii were driven almost entirely by advection (Fig.~\ref{fig:stab-24-48}b); vertical turbulence (Fig.~\ref{fig:stab-24-48}c) and radiation (Fig.~\ref{fig:stab-24-48}d) contributed negligibly to the static stability tendencies in this region.

Outside of the eye, the $N^2$ evolution exhibited alternating layers of positive and negative tendencies.
Near and above 18 km existed an upward-sloping region of decreasing $N^2$ that extended out to the 180-km radius.
In this region, neither vertical turbulence nor radiation exhibited negative $N^2$ tendencies; advection was the only forcing for destabilization.
Immediately below this layer was a region of increasing $N^2$, which sloped upward from 17 km near the 30-km radius to just below 18 km outside of the 100-km radius.
Advection and vertical turbulence both contributed to this positive $N^2$ tendency, with advection playing an important role below about 17.5 km and and turbulence playing an important role above.
The sum of advection and turbulence (Fig.~\ref{fig:stab-24-48}e) reveals two discontiguous regions of increasing $N^2$ in the 17-18-km layer rather than one contiguous region.
The addition of radiation to these two terms, however, (Fig.~\ref{fig:stab-24-48}f) provides the link between these two regions, indicating that radiation also plays a role in strengthening the stable layer just above the tropopause.
In the 16-17-km layer, a horizontally-extensive layer of decreasing $N^2$ also was forced by a combination of advection, vertical turbulence, and radiation.
The sum of advection and vertical turbulence accounts for only a portion of the decreasing $N^2$ in this layer, and actually indicates forcing for stabilization near the 50-km radius and outside of the 130-km radius.
Radiative tendencies overcome this forcing for stabilization in both of these regions to produce the radially-extensive region of destabilization observed just below the tropopause.

@@

Diurnal variability of of static stability in the upper troposphere is an interesting area of future research.

% text...
% \section{Section title}
